TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-05-25 main.tex
results
MC
Added add pooling to GNNs.

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}   &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
		& \text{GIN-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			\bottomrule
	\end{tabular}}
\end{table*}

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Triangles}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
							   \scriptsize $\pm   \pm $       & \scriptsize $\pm   \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\

			& \text{GR}            &   \scriptsize $\pm    \pm  $       &   \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\  
			& \text{SP}             &    \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$  \\   
			\cmidrule{2-7}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GINE-$\varepsilon$}         &    \scriptsize $\pm  \pm $       & \scriptsize $\pm \pm $ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ \\
			& \text{GINE-$\varepsilon$-JK}            &    \scriptsize $\pm \pm$       & \scriptsize $\pm \pm$ & \scriptsize $\pm \pm$ &  \scriptsize $\pm \pm$ & \scriptsize $\pm \pm $  \\
			\bottomrule
	\end{tabular}}
\end{table*}

\begin{table}[t]\centering		
	\caption{Results for neural and kernel baselines.}
	\label{t2l}	
	\resizebox{0.55\columnwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcc@{}}	\toprule

>>>>

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule

			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &   $52.3$ \scriptsize $\pm 0.7 \pm 6.7 $       & $72.6$ \scriptsize $\pm  0.6 \pm 4.1$ &  $50.3$ \scriptsize $\pm 0.8 \pm  3.8 $ & $84.5$ \scriptsize $\pm 0.3 \pm 1.7$ & $72.8$ \scriptsize $\pm 0.8 \pm  3.9 $ & $73.9$ \scriptsize $\pm 0.6 \pm 3.2$  \\
%				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
%				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{WLOA} & $58.4$ \scriptsize $\pm 2.0 \pm 7.4$       &  $73.2$ \scriptsize $\pm 0.8 \pm 3.8$ & $49.4$ \scriptsize $\pm 0.3 \pm 3.6 $ & $85.4$ \scriptsize $\pm  0.2 \pm 1.4$ & $73.2$ \scriptsize $\pm 0.6 \pm 3.5$ & $88.4$ \scriptsize $\pm 0.4 \pm 2.1 $   \\
				& \text{GR}            &    $30.1$ \scriptsize $\pm 0.8 \pm 6.0$       & $59.0$ \scriptsize $\pm 0.9 \pm 5.7$ & $39.6$ \scriptsize $\pm 0.5 \pm 3.6  $ & $66.2$ \scriptsize $\pm 0.2\pm 2.2$ & $71.4$ \scriptsize $\pm 0.6\pm 4.4 $ & $60.0$ \scriptsize $\pm 0.2 \pm  2.7$   \\
				& \text{SP}            & $40.5$  \scriptsize $\pm 1.6 \pm 6.2$       & $58.7$ \scriptsize $\pm 0.9 \pm 4.6 $ & $39.5$ \scriptsize $\pm 0.9 \pm 4.2$ & $74.5$ \scriptsize $\pm 0.4\pm 2.2 $  &$75.9$ \scriptsize $\pm 0.6 \pm 4.0$ & $84.6$ \scriptsize $\pm0.2\pm 0.4 $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GINE-$\varepsilon$}   &   \scriptsize $\pm \pm $       & $72.4$ \scriptsize $\pm 0.6\pm 4.0 $ &  $49.7$ \scriptsize $\pm 0.2 \pm  3.9$ & $79.0$ \scriptsize $\pm  0.5 \pm 1.9 $ &  $71.3$ \scriptsize $\pm 0.4 \pm 4.0$ & $90.0$ \scriptsize $\pm 0.6 \pm 1.7 $   \\
		& \text{GINE-$\varepsilon$-JK} &     \scriptsize $\pm \pm $       & $73.4$ \scriptsize $\pm 0.6\pm 4.4$ & $50.6$ \scriptsize $\pm 0.5 \pm 4.2 $ & $79.1$ \scriptsize $\pm  0.2 \pm 1.5 $ & $72.4$ \scriptsize $\pm 0.6 \pm 1.7 $ & $90.6$ \scriptsize $\pm 0.2 \pm  2.2$   \\
		\bottomrule
	\end{tabular}}
\end{table*}

\begin{table*}[t]\centering		
	\caption{Classification accuracies in percent and standard deviations,  \textsc{OOT}--- Computation did not finish within one day, \textsc{OOM}--- Out of memory.}
	\label{t2l}	
	\resizebox{0.75\textwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lccccc@{}}	\toprule
			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{5}{c}{\textbf{Dataset}}\\\cmidrule{3-7}
			& & {\textsc{Mcf-7}}         &  {\textsc{Molt-4}}      & {\textsc{Yeast}}           & {\textsc{github\_stargazers}}       & {\textsc{reddit\_threads}}      \\	\toprule
							\multirow{3}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}    & 
							   $94.5$ \scriptsize $\pm  0.0 \pm 0.4$       &$94.6$ \scriptsize $\pm 0.1  \pm 0.3$ & $$ \scriptsize $\pm \pm$ &  $63.9$ \scriptsize $\pm 0.1\pm1.3$ &$77.0$ \scriptsize $\pm 0.0\pm0.3$  \\

			& \text{GR}            & $91.7$  \scriptsize $\pm  0.0  \pm 0.5 $       & $92.1$ \scriptsize $\pm 0.0 \pm 0.4$ & $$ \scriptsize $\pm  \pm $ &  $53.5$ \scriptsize $\pm 0.0 \pm1.3$ & $51.2$ \scriptsize $\pm 0.0 \pm 0.4$  \\  
			& \text{SP}             &  $91.7$  \scriptsize $\pm 0.0 \pm 0.4 $       &$92.1$  \scriptsize $\pm 0.0 \pm 0.4 $ & $$ \scriptsize $\pm  \pm $ & $64.1$ \scriptsize $\pm 0.1\pm1.4$ & $77.3$ \scriptsize $\pm 0.0 \pm0.3$  \\   
			\cmidrule{2-7}	
	\multirow{2}{*}{\rotatebox{90}{GNN}}	&  \text{GIN-E-$\varepsilon$}         &  $92.0$ \scriptsize $\pm  0.1\pm 0.6$       & $92.3$ \scriptsize $\pm0.1 \pm 0.6$ & \scriptsize $\pm \pm$ &  67.1 \scriptsize $\pm 0.5 \pm 1.6  $ & 77.2 \scriptsize $\pm 0.0  \pm 0.3$ \\
	& \text{GINE-$\varepsilon$-JK}   &   $91.8$ \scriptsize $\pm 0.0\pm 0.5$       & $92.2$ \scriptsize $\pm 0.0\pm0.5$ & \scriptsize $\pm \pm$ &  67.2 \scriptsize $\pm 0.4 \pm 1.3$ &  77.3  \scriptsize $\pm 0.0 \pm 0.3 $  \\
\bottomrule
	\end{tabular}}
\end{table*}

\begin{table}[t]\centering	
	\cm{Maybe add qm9}	
	\caption{Results for neural and kernel baselines.}
	\label{t2l}	
	\resizebox{0.55\columnwidth}{!}{ 	\renewcommand{\arraystretch}{1.1}
		\begin{tabular}{@{}c <{\enspace}@{}lcc@{}}	\toprule
